Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-24 crass/crassnew.tex
Fixing some comments from Fred to crassnew

\begin{definition}%[Replicated designs]
\label{rep.designs}
Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of dimensions of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$) the subset of dimensions of points in $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

@@

Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point. The quality of any $(t,m,s)$-net is therefore measured by the parameter $t$, called $t$-value.

@@

In addition, Sobol' sequences have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under $\oplus$:
\begin{equation}
\begin{gathered}
\vx = \left(\sum_{k=1}^m x_{1,k}2^{-k},\dots,\sum_{k=1}^m x_{s,k}2^{-k}\right)^\intercal\; , \qquad \vz = \left(\sum_{k=1}^m z_{1,k}2^{-k},\dots,\sum_{k=1}^m z_{s,k}2^{-k}\right)^\intercal, \\
\vx\oplus\vz := \left(\sum_{k=1}^m (x_{1,k}+z_{1,k}\mod 2)2^{-k},\dots,\sum_{k=1}^m (x_{s,k}+z_{s,k}\mod 2)2^{-k}\right)^\intercal.
\end{gathered}
\label{group.operation}
\end{equation}
From equation \eqref{dig.net.eq.} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$, with $\mathbb{F}_2:=\{0,1\}$ the Galois field.

@@

To analyze the space-filling properties of both approaches we will use two criteria. The first one is the $L_2$ star discrepancy that measures the uniformity of a point set. This criterion can be easily computed through an analytical expression provided by \cite{Morokoff}. The lower the criterion, the more uniform the point set is. Sobol' sequences were originally constructed to be low discrepancy sequences and therefore, behave well under this criterion. The second criterion is called maximin distance and measures the regularity of a point set. It returns the minimum of all euclidean distances between pairs of points in the set. The higher the criterion, the more spread the point set is.

@@

We name by design $M$ (resp. $A$) one of the two replicated designs constructed with the multiplicative (resp. additive) approach. We set the input space dimension $s$ to $6$. Design $M$ is refined until $\ell=12$, and design $A$ is constructed with an initial value $r=8$ and refined 15 times.  We construct $100$ designs $M$ and $A$ whose average criteria are presented in Figure \ref{results.crit}. Each of the $100$ designs $M$ is independently randomized by applying Owen's scrambling \cite{OwenScrambling}. Each of the $100$ designs $A$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and the vectors $\ve_\ell$ as in equation (\ref{dig.shift}). We also represent in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $A$. The x-axis corresponds to the number of points $N$ of the design. The y-axis corresponds to the value of the criterion. A logarithmic scale is used for both axis.

>>>>

\begin{definition}%[Replicated designs]
\label{rep.designs}
Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of elements of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$) the subset of elements of points in $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{definition}

@@

Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume $b^{t-m}$ will enclose the same proportion of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point. The quality of any $(t,m,s)$-net is therefore measured by the parameter $t$, called $t$-value.

@@

In addition, Sobol' sequences have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under $\oplus$:
\begin{equation}
\begin{gathered}
\vx = \left(\sum_{k=1}^m x_{1,k}2^{-k},\dots,\sum_{k=1}^m x_{s,k}2^{-k}\right)^\intercal\; , \qquad \vz = \left(\sum_{k=1}^m z_{1,k}2^{-k},\dots,\sum_{k=1}^m z_{s,k}2^{-k}\right)^\intercal, \\
\vx\oplus\vz := \left(\sum_{k=1}^m (x_{1,k}+z_{1,k}\mod 2)2^{-k},\dots,\sum_{k=1}^m (x_{s,k}+z_{s,k}\mod 2)2^{-k}\right)^\intercal.
\end{gathered}
\label{group.operation}
\end{equation}
From equation \eqref{dig.net.eq.} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$.

@@

To analyze the space-filling properties of both approaches we will use two criteria. The first one is the $L_2$ star discrepancy that measures the uniformity of a point set. This criterion can be easily computed through an analytical expression provided by \cite{Morokoff}. The lower the criterion, the more uniform the point set is. Sobol' sequences were originally constructed to be low discrepancy sequences and therefore, behave well under this criterion. The second criterion is called maximin distance and measures the regularity of a point set. It returns the minimum of all Euclidean distances between pairs of points in the set. The higher the criterion, the more spread the point set is.

@@

We name by design $M$ (resp. $A$) one of the two replicated designs constructed with the multiplicative (resp. additive) approach, and set the input space dimension $s$ to $6$. For design $M$, we study the properties of $\mathcal{P}_8,\dots,\mathcal{P}_{12}$, and for design $A$, we set the initial value to $r=8$ and study the properties of $\mathcal{P}_0,\dots,\mathcal{P}_{15}$. For both $M$ and $A$ we generate $100$ random designs whose average criteria are presented in Figure \ref{results.crit}. While each of the $100$ designs $M$ is independently randomized applying Owen's scrambling \cite{OwenScrambling}, designs $A$ are constructed by randomly selecting matrix $L$ (uniformly among all $2^{r(r-1)/2}$ choices) and vectors $\ve_\ell$ used in equation (\ref{dig.shift}). In addition, we also show in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points as in design $A$. The x-axis corresponds to the number of design points $N$ and the y-axis to the value of the criterion.
